An Improved ANS Transaction Template

### 2018-01-26 paper.tex
done with the experiement description

\subsection{the simulation}
The simulation is build to layer up the different cascade in order to produce
HEU. The different layers of cascade will be called levels in the following. The
first task has been to determine the number of level required to produce HEU.
The optimum number of cascade per level is determine (the same way) that the
centrifuges are distributed on the different cascade stages.
Once both the number of levels and the number of cascades per level is
determined, the simulation is ran.

>>>>

\subsection{Level optimisation}
A last round of optimisation if then ran in order to limit the number of cascade
level to the amount of level required produce HEU, and then to populate the
different level with a total of 30 cascades in order to maximize the HEU
production rate.
